A holomorphic approach to branes in twisted~$M$-theory

### 2022-08-24 fivebranes/finite.tex
merge

\subsection{Local characters for twisted superconformal theories}\label{s:localchar}

Suppose that $\cF$ is the factorization algebra of observables of a topological-holomorphic theory on $\R^m \times \C^n$. 
The local character $\chi_\cF ({\bf q})$ is, by definition, the graded character of algebra of local operators $\cF(0)$ with respect to some group of symmetries \cite{SWchar}.
The particular group of symmetries depends on the theory, so we will present some examples.

The holomorphic twist of the superconformal algebra in dimension six is $\lie{osp}(6|2)$. 
In the case of the holomorphic twist of a six-dimensional superconformal theory we will consider the local character of operators with respect to the subalgebra 
\beqn\label{eqn:cartan2}
\lie{sl}(3) \times \lie{sl}(2) \times \lie{gl}(1) \subset \lie{osp}(6|2) 
\eeqn
and denote the corresponding fugacities by $t_1,t_2,r,q$ just as in \S \ref{sec:states} in our computation of the index of twisted supergravity states.
We recalled in \S \ref{sec:states} an alternative parametrization of the fugacities in terms of the parameters $y_1,y_2,y_3,y,q$ which satisfy the constraint $y_1 y_2 y_3 = 1$.
These parameters are related by $y_1=t_1^{-1}, y_2 = t_1 t_2^{-1}, y_3 = t_2$ and $y = q^{1/2} r$.

Note that for local operators which are the symmetric algebra of some graded vector space we can compute, as usual, the character as the plethystic exponential of a the single particle local character. 
That is, the character of linear local operators.

@@

\parsec
There are various degenerations, or specializations, of this character which are interesting to consider.
A particularly meaningful one is related to two different deformations of the theory by elements in the (twisted) superconformal algebra.
Recall that after performing the holomorphic twist the residual superconformal algebra is~$\lie{osp}(6|2)$.
We have recalled in \ref{s:global1} how the bosonic part of this algebra is represented by fields of the eleven-dimensional theory.

There are two types of odd elements of~$\lie{osp}(6|2)$ that also have a natural interpretation in the eleven-dimensional theory.
The odd part of~$\lie{osp}(6|2)$ can be identified with 
\[
\C^3 \otimes \C^2 \oplus \wedge^2(\C^3) \otimes \C^2 
\]
where $\C^3, \C^2$ are the fundamental $\lie{sl}(3)$ and $\lie{sl}(2)$ representations, respectively.

>>>>

@@

\parsec
There are various degenerations, or specializations, of this character which are interesting to consider.
A particularly meaningful one is related to two different deformations of the theory by elements in the (twisted) superconformal algebra.
Recall that after performing the holomorphic twist the residual superconformal algebra is~$\lie{osp}(6|2)$.
We have recalled in \S\ref{s:global1} how the bosonic part of this algebra is represented by fields of the eleven-dimensional theory.

There are two types of odd elements of~$\lie{osp}(6|2)$ that also have a natural interpretation in the eleven-dimensional theory.
The odd part of~$\lie{osp}(6|2)$ can be identified with the twelve-dimensional space
\[
\C^3 \otimes \C^2 \oplus \wedge^2(\C^3) \otimes \C^2 
\]
where $\C^3, \C^2$ are the fundamental $\lie{sl}(3)$ and $\lie{sl}(2)$ representations, respectively. 
The $\lie{gl}(1)$ factor in the bosonic part of $\lie{osp}(6|2)$ acts with weight $1/2$ on both summands.

### 2022-08-24 fivebranes/ops.tex
merge

In this section we recall the essentials of the theory of local operators for holomorphic-topological theories. 
We consider a way of counting operators in a topological-holomorphic theory, called the `local character' of a holomorphic-topological theory \cite{SWchar}, and compare it to the superconformal index.
We will then present a few examples including expressions for the local character on the twists of a theory on a single membrane and fivebrane and will find the expected match with the physics literature.

@@

\subsection{A relationship to the superconformal index}

We will turn to computing the local character for twists of the single membrane and fivebrane theories momentarily and comment on the relationship to known formulas in the physics literature. 
First, we point out a general relationship between the local character as we've defined it and the superconformal index.

The superconformal index of a superconformal field theory is the Witten index of the theory in the radial quantization.
Explicitly, if the theory lives in a $d$-dimensional space time and $\cH$ denotes the Hilbert space on $S^{d-1}$, then the index is
\beqn
\cI(q,x_1,\ldots,x_n) = \Tr_{\cH} (-1)^F q^{\delta} x_1^{G_1} \cdots x_n^{G_n} 
\eeqn
where $\{G_i\}$ are a collection of charges that commute with a particular subset of elements of the superconformal algebra. 
We can choose that each $G_i$ commute with a minimal supercharge $Q$ and its adjoint $Q^{\dagger}$ in the superconformal algebra.
Necessarily the $G_i$ also commute with $\delta = [Q,Q^{\dagger}]$.
After tracing over $\cH$ one can identify the superconformal index with the partition function of the model on a space which is topologically equivalent to~$S^{d-1} \times S^1$.

The Witten index is protected under twisting---in our setup the index $\cI(q,x_1,\ldots,x_n)$ can be computed in the minimal twist of the superconformal theory we start with.
Let us specialize to the case of the six-dimensional superconformal index. 
In this case, we choose our fugacities to be $x_1 = t_1, x_2 = t_2$ and $x_3 = r$ as generators for the Cartan in the twisted superconformal algebra, see equation \eqref{eqn:cartan2}.

The minimal twist of the Hilbert space $\cH^Q$ is exactly the space of holomorphic local operators at $0$ in $\C^3$, for details see~\cite{SWchar}. 
Thus, the index $\cI(q,t_1,t_2,r)$ agrees with the holomorphic character $\chi(q,t_1,t_2,r)$.

>>>>

In this section we recall the essentials of the theory of local operators for holomorphic-topological theories. 
We consider a way of counting operators in a topological-holomorphic theory, called the `local character' of a holomorphic-topological theory \cite{SWchar}, and compare it to the superconformal index.
We then present a few simple examples and then go on to set up the theory of local operators associated to factorization algebras~$\clie_\bu(\cG_{N,c})$ we constructed in \S \ref{s:fact}.

@@

\subsection{Local characters for twisted superconformal theories}\label{s:localchar}

Suppose that $\cF$ is the factorization algebra of observables of a topological-holomorphic theory on $\R^m \times \C^n$. 
The local character $\chi_\cF ({\bf q})$ is, by definition, the graded character of algebra of local operators $\cF(0)$ with respect to some group of symmetries \cite{SWchar}.
The particular group of symmetries depends on the theory.
In this section we focus on local characters of factorization algebras that arise as twists of six-dimensional $\cN=(2,0)$ supersymmetric theories.

The (complexified) superconformal algebra in dimension six is $\lie{osp}(8|4)$. 
The holomorphic twist of this superconformal algebra is $\lie{osp}(6|2)$. 
We will consider the symmetry by the bosonic subalgebra
\beqn\label{eqn:cartan3}
\lie{sl}(3) \times \lie{sl}(2) \times \lie{gl}(1) \subset \lie{osp}(6|2)  .
\eeqn
The corresponding generators of the Cartan, as in \S \ref{sec:states}, were denoted $h_1,h_2,h,$ and $\Delta$ and the respective fugacities $t_1,t_2,r,q$.

We have described how this subalgebra embeds as fields in the twist of eleven-dimensional supergravity in \S \ref{s:ads7}. 
In particular, the holomorphic twist of any six-dimensional superconformal theory will have as a symmetry the subalgebra \eqref{eqn:cartan3}.
If the corresponding factorization algebra is $\cF$, and the local operators $\cF(0)$, the local character is then defined by the formal expression
\beqn
\chi_{\cF}(t_1,t_2,r,q) = {\rm Tr}_{\cF(0)} \left((-1)^F t_1^{h_1} t_2^{h_2} r^h q^\Delta\right) .
\eeqn
In the next section we will compute these characters in the case that the factorization algebra $\cF$ is $\clie_\bu(\cG_{N,c})$ where $N = 1,2,\ldots$.

We pointed out in \S \ref{sec:states} an alternative parametrization of the fugacities in terms of the parameters $y_1,y_2,y_3,y,q$ which satisfy the constraint $y_1 y_2 y_3 = 1$.
These parameters are related by $y_1=t_1^{-1}, y_2 = t_1 t_2^{-1}, y_3 = t_2$ and $y = q^{1/2} r$. 
We will also consider formulas for the local character in terms of these variables.

%Note that for local operators which are the symmetric algebra of some graded vector space we can compute, as usual, the character as the plethystic exponential of a the single particle local character. 
%That is, the character of linear local operators.

\subsection{A relationship to the superconformal index}
\label{sec:sucaindex}
There is a general relationship between the local character for the holomorphic twist of six-dimensional $\cN=(2,0)$ supersymmetric theories and the more well-studied superconformal index.

The superconformal index of a superconformal field theory is the Witten index of the theory in the radial quantization.
In our situation we look at the Hilbert space $\cH$ of the theory on $S^{5}$ and consider the index heuristically of the form
\beqn
\Tr_{\cH} (-1)^F  x_1^{G_1} \cdots x_n^{G_n} q^{\Delta}
\eeqn
where $\{G_i\}$ are a collection of charges that commute with the holomorphic supercharge $Q$ and its superconformal adjoint $S = Q^\dagger$. 
Here, $\Delta = [Q,S]$.
We choose three elements $G_1,G_2,G_3$ in such a way that they become the elements $h_1,h_2,h$ upon taking $Q$-cohomology (and so automatically commute with $Q$ and $S$). 
Thus we consider the following index
\beqn
\cI (t_1,t_2,r,q) \define \Tr_{\cH} (-1)^F t_1^{h_1} t_2^{h_2} r^h q^\Delta .
\eeqn
After tracing over $\cH$ one can identify the superconformal index with the partition function of the model on a space which is topologically equivalent to~$S^{5} \times S^1$.

The Witten index is protected under twisting---in our setup the index $\cI(t_1,t_2,r,q)$ can be computed in the minimal twist of the superconformal theory we start with.
The minimal twist of the Hilbert space $\cH^Q$ is exactly the space of holomorphic local operators at $0$ in $\C^3$, for details see~\cite{SWchar}. 
Thus, the index $\cI(t_1,t_2,r,q)$ agrees with the holomorphic character $\chi(t_1,t_2,r,q)$ defined above.
